{\fontfamily{ptm}\selectfont Nesterov Type Momentum Methods}

### 2024-06-14 Notebook LaTEX/Momentum Accelerations/main.tex
>w< ok we are back

            \par\noindent 
            We need to observe the case where $t = 0$ to understand the base case of the algorithm. 
            At each iteration $t$, Given $(x_t, y_t)$, the above formula maps to $(x_{t + 1}, y_{t + 1}, z_{t + 1})$. 
            When $t= 0$, it has $y_1 = x_1$. 
            Therefore, knowing only either $y_1$, or $x_1$ can initiate the algorithm. 
            This is an alternative scenario of the base case. 
            If, we wish to write $y_0 = x_0$ at $t = 0$ for the base case instead, then it creates the following algorithm 
            \begin{align*}
                y_{t} &= \left(
                1 - \frac{2}{t + 2} 
                \right)z_{t} + 
                \left(
                    \frac{1}{t + 2}
                \right)x_{t}, 
                \\
                z_{t + 1} &= y_t + L^{-1}\nabla f(y_t), 
                \\
                x_{t + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t). 
            \end{align*}
            It has a different representations due to a specific choice of the base case. 
            \par\noindent
            Finally, by the observation that given $(z_t, y_t)$ for any $t\ge -1$, we can solve for $x_t$ \newline via $y_t = (1 - 2/(1 + t))z_t + 1/(t + 1)x_t$, obtaining $(x_t, y_t, z_t)$, hence the algorithm can be reduced to a representations with only $(z_t, y_t)$ and an updates using only $(z_t, y_t)$ to $(z_{t + 1}, y_{t + 1})$. 
            That is the momentum form presented above.
        We advise the reader to read the Biliography notes by Ryu \cite[chapter 12]{ryu_large-scale_2022} of his book. 
        It goes over the full context and history for this particular variant of gradient acceleration method. 
        As the time of composing this notes, the writer is still reading on the topic of accelerated gradient. 

@@

            With $\eta_t, \tilde \eta_t$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} where $\eta_{t + 1} = \tilde \eta_{t + 1} = (t - 1)/L$, we derive the following algorithm: 

@@

            To satisfy the equality, reader should verify that $\eta_{t + 1} = (t)/ L$ is one of the options. 

>>>>

            \par\noindent 
            We need to observe the case where $t = 0$ to understand the base case of the algorithm. 
            At each iteration $t$, Given $(x_t, y_t)$, the above formula maps to $(x_{t + 1}, y_{t + 1}, z_{t + 1})$. 
            When $t= 0$, it has $y_1 = x_1$. 
            Therefore, knowing only either $y_1$, or $x_1$ can initiate the algorithm. 
            This is an alternative scenario of the base case. 
            If, we wish to write $y_0 = x_0$ at $t = 0$ for the base case instead, then it creates the following algorithm 
            \begin{align*}
                y_{t} &= \left(
                1 - \frac{2}{t + 2} 
                \right)z_{t} + 
                \left(
                    \frac{1}{t + 2}
                \right)x_{t}, 
                \\
                z_{t + 1} &= y_t + L^{-1}\nabla f(y_t), 
                \\
                x_{t + 1} &= x_t + (t + 1)(2L)^{-1}\nabla f(y_t). 
            \end{align*}
            It has a different representations due to a specific choice of the base case. 
            \par\noindent
            Finally, by the observation that given $(z_t, y_t)$ for any $t\ge -1$, we can solve for $x_t$ \newline via $y_t = (1 - 2/(1 + t))z_t + 1/(t + 1)x_t$, obtaining $(x_t, y_t, z_t)$, hence the algorithm can be reduced to a representations with only $(z_t, y_t)$ and an updates using only $(z_t, y_t)$ to $(z_{t + 1}, y_{t + 1})$. 
            That is the momentum form presented above. 
        \end{observation}
        We advise the reader to read the Biliography notes by Ryu \cite[chapter 12]{ryu_large-scale_2022} of his book. 
        It goes over the full context and history for this particular variant of gradient acceleration method. 
        As the time of composing this notes, the writer is still reading on the topic of accelerated gradient.

@@

            With $\eta_t, \tilde \eta_t$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} where $\eta_{t + 1} = \tilde \eta_{t + 1} = 2/(2L)$, we derive the following algorithm: 

@@

            To satisfy the equality, reader should verify that $\eta_{t} = t/(2L)$ is one of the options. 
